Forecasting future oil production in Norway and the UK: a general improved methodology

### 2014-07-21 Publications/Forecasting  Future Oil Production/Source/manuscript.tex
Latest version.

\maketitle
\begin{abstract}
\noindent We present a new Monte-Carlo methodology to forecast
the crude oil production of Norway and the U.K. based on a two-step process,
(i) the nonlinear extrapolation of the current/past
performances of individual oil fields and (ii) a stochastic model
of the frequency of future oil field discoveries. Compared
with the standard methodology that tends to underestimate remaining oil reserves,
our method gives a better description of future oil production, as validated by
our back-tests starting in 2008. Specifically, we predict remaining reserves
extractable until 2030 to be $5.7 \pm 0.3$ million barrels for Norway and $3.0 \pm0.3$ billion
barrels for the UK, which are respectively $45\%$ and $66\%$ above the
predictions using an extrapolation of aggregate production.
\end{abstract}

>>>>

\maketitle
\begin{abstract}
\noindent We present a new Monte-Carlo methodology to forecast
the crude oil production of Norway and the U.K. based on a two-step process,
(i) the nonlinear extrapolation of the current/past
performances of individual oil fields and (ii) a stochastic model
of the frequency of future oil field discoveries. Compared
with the standard methodology that tends to underestimate remaining oil reserves,
our method gives a better description of future oil production, as validated by
our back-tests starting in 2008. Specifically, we predict remaining reserves
extractable until 2030 to be $5.7 \pm 0.3$ billion barrels for Norway and $3.0 \pm0.3$ billion barrels for the UK, which are respectively $45\%$ and $66\%$ above the predictions using an extrapolation of aggregate production.
\end{abstract}
